Phase paper outline your mom last night

### 2014-05-23 Manuscript/Phase_detectors_outline.tex
Added a bibliography. Added a Tables subsection to the outline. The Muller folder is a bullshit temp folder but I am too lazy to deal with it now.

\subsection*{Potential physiology journals}

\begin{itemize}
\item Acta physiologica
\item Physiological Reports
\item AJP Heart/regulatory - Innovative methodology
\item The Journal of Physiology - techniques for physiology \textit{I think this kind of thing might be best}
\item The Journal of General Physiology - methods and approaches
\item Physiological measurement
\item Journal of experimental physiology
\end{itemize}

@@

Homeostasis is maintained by numerous interacting physiological control systems. Physiological systems are responsible for controlling a given output variable in response to one or more input variables. For example Heart rate is controlled by the autonomic nervous system to maintain blood pressure. Nonlinear responses between input and output in physiological systems are ubiquitous. Furthermore there are inherent delays in the response of each system because of inter and intra cellular signalling events. These nonlinearities

@@

>>>>

\subsection*{Potential physiology journals}
The paper should have this structure:\cite{muller_estimation_2003}
\begin{itemize}
\item Acta physiologica
\item Physiological Reports
\item AJP Heart/regulatory - Innovative methodology
\item The Journal of Physiology - techniques for physiology \textit{I think this kind of thing might be best}
\item The Journal of General Physiology - methods and approaches
\item Physiological measurement
\item Journal of experimental physiology
\item Journal of Applied Phyiology
\item E-Life
\end{itemize}

@@

@@

	\subsection*{Tables}
		\begin{enumerate}
			\item Simulation
			\begin{enumerate}
			\item Noise conversation
				\begin{itemize}
					\item Add gaussian noise from snr=$\infty$ up to when it breaks down.
					\item It breaks down when 0 is not in the 95\% confidence interval of Bland-Altman-style statistics.		
				\end{itemize}
			\item Chirp (Frequency from point A to point B)
				\begin{itemize}
					\item Specifically to talk about limits to the bandpass filtering needed for the Hilbert method.
				\end{itemize}
			\item Length of signal
				\begin{itemize}
					\item Shorten the signal until techniques breakdown.
					\item Relative to frequency.
				\end{itemize}		
			\end{enumerate}
			\item Physiological Data

		\end{enumerate}

\bibliographystyle{plain}
\bibliography{OutlineBib}
